Refunctionalization of Abstract Abstract Machines (Functional Pearl)

### 2018-06-05 paper/paper.tex
reformat the dots

\begin{lstlisting}
def drive_step(nds: NDState, seen: Set[State]): Set[State] = {
  nds match {
    case NDState(ae, _, _, Nil, _, Nil) if isAtomic(ae) => seen
    case nds =>
      val s = nds.toState
      val new_seen = if (seen.contains(s)) seen else seen+s
      val newTime = nds.tick
      val new_ndstate = nds match {
        case NDState(Let(x, App(f, ae), e), env, bstore, konts, time, ndkonts) =>
          ......
        case NDState(ae, env, bstore, konts, time, ndkonts) if isAtomic(ae) =>
          ......
      }
      drive_step(new_ndstate, new_seen)
  }
}
\end{lstlisting}

@@

\begin{lstlisting}
def drive_step(nds: NDState, seen: Set[State]): Set[State] = {
  nds match {
    case NDState(ae, _, _, Nil, _, Nil) if isAtomic(ae) => seen
    case nds =>
      val s = nds.toState
      val new_seen = if (seen.contains(s)) seen else seen + s
      val new_time = nds.tick
      nds match {
        case NDState(Let(x, App(f, ae), e), env, bstore, konts, time, ndk) =>
          ......
          drive_step(NDState(body, new_env, new_store, new_frames, new_time, new_ndk), new_seen)
        case NDState(ae, env, bstore, konts, time, ndk) if isAtomic(ae) =>
          continue(nds, new_seen)
      }
  }
}
\end{lstlisting}

@@

\begin{lstlisting}
type Cont = Ans => Ans
def aeval(e: Expr, env: Env, store: BStore, time: Time, continue: Cont): Ans = {
  val new_time = ......
  e match {
    case Let(x, App(f, ae), e) => ......
    case ae if isAtomic(ae) => ......
  }
}
\end{lstlisting}

@@

\begin{lstlisting}
def aeval(e: Expr, env: Env, store: BStore, time: Time, cache: Cache, continue: Cont): Ans = {
  val config = Config(e, env, store, time)
  /* lookups the out cache, uses the values if contains this config */
  if (cache.outContains(config)) cont(Ans(cache.outGet(config), cache))
  else {
    val new_cache = cache.outUpdate(config, cache.inGet(config))
    val new_time = config.tick 
    e match {
      case Let(x, App(f, ae), e) =>
        val closures = atomicEval(f, env, store)
        nd[Storable](closures, Ans(Set[VS](), new_cache), {
          case (Clos(Lam(v, body), c_env), clsans, clsnd) =>
            ...... /* sets vairables, e.g., new_cenv and new_store */
            aeval(body, new_cenv, new_store, new_time, clsans.cache, { case Ans(bdvss, bdcache) =>
              nd[VS](bdvss, Ans(Set[VS](), bdcache), {
                case (VS(vals, time, vssstore), bdans, bdnd) =>
                  ...... /* sets variables, e.g., new_env and new_store */
                  aeval(e, new_env, new_store, time, bdans.cache, {
                    /* updates the out cache after evaluated to the end of one path  */
                    case Ans(evss, ecache) => bdnd(bdans ++ Ans(evss, ecache.outUpdate(config, evss)))
                  })
              }, { case eans => clsnd(eans ++ clsans) })
            })
        },
        continue)

>>>>

\begin{lstlisting}
def drive_step(nds: NDState, seen: Set[State]): Set[State] = {
  nds match {
    case NDState(ae, _, _, Nil, _, Nil) if isAtomic(ae) => seen
    case nds =>
      val s = nds.toState
      val new_seen = if (seen.contains(s)) seen else seen+s
      val newTime = nds.tick
      val new_ndstate = nds match {
        case NDState(Let(x, App(f, ae), e), env, bstore, konts, time, ndkonts) =>
          ...
        case NDState(ae, env, bstore, konts, time, ndkonts) if isAtomic(ae) =>
          ...
      }
      drive_step(new_ndstate, new_seen)
  }
}
\end{lstlisting}

@@

\begin{lstlisting}
def drive_step(nds: NDState, seen: Set[State]): Set[State] = {
  nds match {
    case NDState(ae, _, _, Nil, _, Nil) if isAtomic(ae) => seen
    case nds =>
      val s = nds.toState
      val new_seen = if (seen.contains(s)) seen else seen + s
      val new_time = nds.tick
      nds match {
        case NDState(Let(x, App(f, ae), e), env, bstore, konts, time, ndk) =>
          ...
          drive_step(NDState(body, new_env, new_store, new_frames, new_time, new_ndk), new_seen)
        case NDState(ae, env, bstore, konts, time, ndk) if isAtomic(ae) =>
          continue(nds, new_seen)
      }
  }
}
\end{lstlisting}

@@

\begin{lstlisting}
type Cont = Ans => Ans
def aeval(e: Expr, env: Env, store: BStore, time: Time, continue: Cont): Ans = {
  val new_time = ...
  e match {
    case Let(x, App(f, ae), e) => ...
    case ae if isAtomic(ae) => ...
  }
}
\end{lstlisting}

@@

\begin{lstlisting}
def aeval(e: Expr, env: Env, store: BStore, time: Time, cache: Cache, continue: Cont): Ans = {
  val config = Config(e, env, store, time)
  /* lookups the out cache, uses the values if contains this config */
  if (cache.outContains(config)) cont(Ans(cache.outGet(config), cache))
  else {
    val new_cache = cache.outUpdate(config, cache.inGet(config))
    val new_time = config.tick 
    e match {
      case Let(x, App(f, ae), e) =>
        val closures = atomicEval(f, env, store)
        nd[Storable](closures, Ans(Set[VS](), new_cache), {
          case (Clos(Lam(v, body), c_env), clsans, clsnd) =>
            ... /* sets vairables, e.g., new_cenv and new_store */
            aeval(body, new_cenv, new_store, new_time, clsans.cache, { case Ans(bdvss, bdcache) =>
              nd[VS](bdvss, Ans(Set[VS](), bdcache), {
                case (VS(vals, time, vssstore), bdans, bdnd) =>
                  ... /* sets variables, e.g., new_env and new_store */
                  aeval(e, new_env, new_store, time, bdans.cache, {
                    /* updates the out cache after evaluated to the end of one path  */
                    case Ans(evss, ecache) => bdnd(bdans ++ Ans(evss, ecache.outUpdate(config, evss)))
                  })
              }, { case eans => clsnd(eans ++ clsans) })
            })
        },
        continue)
